Compilation With Program Synthesis

### 2023-08-30 new-paper/paper.tex
Improve abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics.

  Along the way, we encounter limitations in the \SuSLik{} tool. In confronting these limitations, we develop a new feature
  in \Pika{} that allows the programmer to express synthesis tasks at a higher-level.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics. This translation also makes interfacing between SSL and \Pika{} easy. We introduce ``layouts'' to bridge the gap between a functional programming language and SSL called. This allows us to describe the memory layout of algebraic data types as SSL predicates inside \Pika.

  We then develop a second version of \Pika{} extended with an additional synthesis feature. These two versions are compared.

  % Along the way, we encounter limitations in the \SuSLik{} tool. In confronting these limitations, we develop a new feature
  % in \Pika{} that allows the programmer to express synthesis tasks at a higher-level.
